---
title: "StatPREP Lesson Lessons"
output: 
  html_document:
    theme: readable
---

```{r include = FALSE}
library(littleapp2)
module_format_string <- function(base_name) {
  glue::glue("[web format](Lessons/{base_name}.html) : [pdf format](Lessons/{base_name}.pdf) : [word format](Lessons/{base_name}.docx) : [Rmd format](Lessons/{base_name}.Rmd)")
}
```

## Point Plot

```{r echo = FALSE}
point_plot_app <- get_app_info("point_plot")
jitter_app <- get_app_info("jitter")
center_app <- get_app_info("spread")
t_test_app <- get_app_info("t_test")
rare_app <- get_app_info("rare")
regression_app <- get_app_info("linear")
```

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("point_plot")`

Introduces basics of a point plot: that each row in the data corresponds to one dot in the point plot.

## Variable types

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("point_plot")`

Introduces the distinction between quantitative and categorical variables through their very different appearances in a point plot. Provides some vocabularly, e.g. *levels* of a categorical variable, *ordinal*, the *interval*  from max to min of a quantitative variable, the *spread* of a quantitative variable.

## Variables and the unit of observation

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("variables-and-units")`

Gets students to think about what is the unit of observation in each data set and how to look up the meaning of each variable.

## Jittering

App: [`r jitter_app$name`](`r jitter_app$url`)

This is a simple app that helps introduce jittering by allowing the user to control the amount of jittering on each axis, as well as the transparency.

Question in draft: Do we need a lesson document for this?

## Common shapes of distributions

App: [`r rare_app$name`](`r rare_app$url`)

File: `r module_format_string("distribution-shapes")`

Where terms for describing such as "skew," "bi-modal," "flat," and "normal" are introduced by reference to the difference of the actual variable from a theoretical normal distribution.

## Parameters of the normal distribution

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("normal_parameters")`

## Describing spread with a 95% interval

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("summary_interval")`

## The standard deviation

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("SD_and_summary_interval")`

## Common, rare, standard deviation and z-score

App: [`r rare_app$name`](`r rare_app$url`)

File: `r module_format_string("commmon-and-rare")`

Using the z-score to express concepts of "common" and "rare."

## Response and explanatory variables

App: Several. Links are in the lesson.

File: `r module_format_string("response-and-explanatory")`

Reasons to identify one variable as the response and another as the explanatory.

## Comparing means --  Part I
 
App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("comparing-two-groups")`


Looking at sampling variation with new samples.

## Comparing means --  Part II

App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("comparing-confidence-intervals")`


Comparing the two confidence intervals

## Comparing means --  Part III

App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("Two-sample-t-test")`

Using the t-statistic

## Describing relationship patterns in words and numbers

App: [`r regression_app$name`](`r regression_app$url`)

File: `r module_format_string("relationship-patterns")`

How to summarize the pattern indicated by a regression line.

## How much variation is explained

App: [`r regression_app$name`](`r regression_app$url`)

File: `r module_format_string("how-much-is-explained")`

Introduces the concept of quantifying how much of one variable is accounted for (or "explained") by another.

AND FIGURE OUT WHERE YOU WERE GOING WITH "lesson-2.Rmd"

## Covariates

This will be about how introducing a covarate can change the estimate of the effect size.

## Inference

There will be several inference lessons

## Reading statistical reports

There will be several lessons here, too.

## Strength and significance

Will be about distinguishing between the p-value and the effect size.

Increase sample size and watch  p get smaller. But the effect size isn't getting bigger.

## Density in two variables. 

Look at baby weight versus gestation, and notice a second tail to the cloud at about 30 weeks gestation and 3000 grams. Is there a gap between this tail and the upward-sloping tail. Can you think of an explanation of this second tail in terms of errors in the measurement of the length of gestation. What might lead to such a mistake? How large would it typically be?



## Inference: mean or median? range or standard deviation.

Use the bootstrapping app


