# StatPREP Lesson Modules

```{r include = FALSE}
library(littleapp2)
module_format_string <- function(base_name) {
  glue::glue("[web format](Modules/{base_name}.html) : [pdf format](Modules/{base_name}.pdf) : [word format](Modules/{base_name}.docx) : [Rmd format](Modules/{base_name}.Rmd)")
}
```

## Point Plot

```{r echo = FALSE}
point_plot_app <- get_app_info("point_plot")
jitter_app <- get_app_info("jitter")
```

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("point_plot")`

Introduces basics of a point plot: that each row in the data corresponds to one dot in the point plot.


## Variable types

App: [`r point_plot_app$name`](`r point_plot_app$url`)

Baby weight versus gestation: Why the vertical stripes in gestation? How does jittering gestation change the graph? 

## Jittering

App: [`r jitter_app$name`](`r jitter_app$url`)

## Describing spread

Range. Use measuring stick

## Response and explanatory variables

## Cases, rows, and the unit of observation

## Relative density

## Density in two variables. 

Look at baby weight versus gestation, and notice a second tail to the cloud at about 30 weeks gestation and 3000 grams. Is there a gap between this tail and the upward-sloping tail. Can you think of an explanation of this second tail in terms of errors in the measurement of the length of gestation. What might lead to such a mistake? How large would it typically be?

## Measuring spread

Standard deviation vs range


## "Explaining" the response variable

mother and father's age in Births_2015