# StatPREP Lesson Modules

```{r include = FALSE}
library(littleapp2)
module_format_string <- function(base_name) {
  glue::glue("[web format](Modules/{base_name}.html) : [pdf format](Modules/{base_name}.pdf) : [word format](Modules/{base_name}.docx) : [Rmd format](Modules/{base_name}.Rmd)")
}
```

## Point Plot

```{r echo = FALSE}
point_plot_app <- get_app_info("point_plot")
jitter_app <- get_app_info("jitter")
center_app <- get_app_info("spread")
t_test_app <- get_app_info("t_test")
rare_app <- get_app_info("rare")
```

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("point_plot")`

Introduces basics of a point plot: that each row in the data corresponds to one dot in the point plot.


## Variable types

App: [`r point_plot_app$name`](`r point_plot_app$url`)

File: `r module_format_string("point_plot")`

Introduces the distinction between quantitative and categorical variables through their very different appearances in a point plot. Provides some vocabularly, e.g. *levels* of a categorical variable, *ordinal*, the *interval*  from max to min of a quantitative variable, the *spread* of a quantitative variable.

## Jittering

App: [`r jitter_app$name`](`r jitter_app$url`)

## Common shapes of distributions

App: [`r rare_app$name`](`r rare_app$url`)

File: `r module_format_string("distribution-shapes")`

Where terms for describing such as "skew," "bi-modal," "flat," and "normal" are introduced by reference to the difference of the actual variable from a theoretical normal distribution.

## Parameters of the normal distribution

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("normal_parameters")`

## Describing spread with a 95% interval

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("summary_interval")`


## The standard deviation

App: [`r center_app$name`](`r center_app$url`)

File: `r module_format_string("SD_and_summary_interval")`


## next
Range. Use measuring stick

Baby weight versus plurality, covar sex

## Response and explanatory variables

## Cases, rows, and the unit of observation

## Comparing two means (Part I)

App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("Comparing-two-groups")`


Looking at sampling variation with new samples.

## Comparing two means  (Part II)

App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("Comparing-confidence-intervals")`


Comparing the two confidence intervals

## Comparing two  means  (Part III)

App: [`r t_test_app$name`](`r t_test_app$url`)

File: `r module_format_string("Two-sample-t-test")`

Using the t-statistic

## Relative density

## Density in two variables. 

Look at baby weight versus gestation, and notice a second tail to the cloud at about 30 weeks gestation and 3000 grams. Is there a gap between this tail and the upward-sloping tail. Can you think of an explanation of this second tail in terms of errors in the measurement of the length of gestation. What might lead to such a mistake? How large would it typically be?

## Measuring spread

Standard deviation vs range

## Relationships

mother and fathers age versus mother and fathers weight: which has a closer relationship?



## "Explaining" the response variable

mother and father's age in Births_2015

## Inference: mean or median? range or standard deviation.

Use the bootstrapping app